A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2015-10-24 imaging_demo/ms.tex
Add abstract
From 95fd8c8 (master):
=====================

In ms.tex,

(*) Add abstract

% Abstract of the paper
\begin{abstract}
Abstract here (250 words)
\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
Modern radio telescopes are marching towards densely packed array layouts 
consisting of a large number of antennas ($N$). Since the cost of traditional 
correlators scales as $\mathcal{O}(N^2)$, there will be a steep cost for 
realizing the full imaging potential of these powerful instruments. Through 
our generic and efficient E-field Parallel Imaging Correlator (EPIC), we present 
the first software demonstration of a generalized direct imaging algorithm 
known by the name Modular Optimal Frequency Fourier (MOFF) imager. It takes 
advantage of the multiplication-convolution theorem of Fourier transform. Not 
only does it bring down the cost to $\mathcal{O}(N\log N)$ but can also image 
from irregularly arranged antenna arrays. EPIC is highly modular and 
parallelizable. It is implemented in object oriented Python and is publicly 
available. We have verified the images produced to be mathematically identical 
to those produced using traditional techniques. We have also validated our 
implementation on data observed with the Long Wavelength Array. Antenna systems
with a dense filling factor consisting of a large number of antennas such as 
LWA, SKA, and HERA will gain a significant advantage by deploying EPIC. 
Inherent availability of calibrated time-domain images on timescales roughly 
equal to the writeout timescale of the digitizer will make it a prime 
candidate for transient searches of primarily Fast Radio Bursts (FRB) as well 
as slower planteary and exoplantenary phenomena. 
\end{abstract}
